A quantum parallel Markov chain Monte Carlo

### 2022-03-16 main.tex
corrected qpmcmc algorithm

\doublespacing

@@

%\author{Andrew J.~Holbrook}

%\affil{UCLA Biostatistics}

\author{}

@@

\begin{algorithm}[t!]
	\caption{Quantum parallel MCMC}\label{alg:qpMCMC}
	\KwData{Initial Markov chain state $\ttheta^{(0)}$; total length of Markov chain $S$; total number of proposals per iteration $P$; routine for evaluating target density $\pi(\cdot)$; routines for drawing random samples from a $D$-dimensional multivariate Gaussian $Normal_D(\boldsymbol{\mu},\SSigma)$ and the standard Gumbel distribution $Gumbel(0,1)$.}
	\KwResult{A Markov chain $\ttheta^{(1)}, \dots, \ttheta^{(S)}$.}
	\For{$s \in\{1,\dots,S\}$}{
		$\ttheta_0 \gets \ttheta^{(s-1)}$\;
		$\bar{\ttheta} \gets Normal_D(\ttheta_0,\SSigma)$; \hspace{14em} \Comment{ \hspace{0.3em}     Proposal \eqref{eq:p1}}      
		\For{$p \in \{0,\dots,P\}$}{
			$\ttheta_p \gets Normal_D(\bar{\ttheta},\SSigma)$\;
			$z_{p} \gets Gumbel(0,1)$\;
		}
		$\hat{p} \gets \argmin_{p=0,\dots,P}\Big(f(p):= -\big(z_{p}+ \log\pi(\ttheta_{p}) \big)\Big)$; \hspace{3.5em} \Comment{$\order{\sqrt{P}}$ Alg \ref{alg:min}}
		$\ttheta^{(s)} \gets \ttheta_{\hat{p}}$\;
	}
	\Return{$\ttheta^{(1)}, \dots, \ttheta^{(S)}$}\ .

>>>>

%\doublespacing

@@

\author{Andrew J.~Holbrook}

\affil{UCLA Biostatistics}

%\author{}

@@

\begin{algorithm}[t!]
	\caption{Quantum parallel MCMC}\label{alg:qpMCMC}
	\KwData{Initial Markov chain state $\ttheta^{(0)}$; total length of Markov chain $S$; total number of proposals per iteration $P$; routine for evaluating target density $\pi(\cdot)$; routines for drawing random samples from a $D$-dimensional multivariate Gaussian $Normal_D(\boldsymbol{\mu},\SSigma)$ and the standard Gumbel distribution $Gumbel(0,1)$.}
	\KwResult{A Markov chain $\ttheta^{(1)}, \dots, \ttheta^{(S)}$.}
	\For{$s \in\{1,\dots,S\}$}{
		$\ttheta_0 \gets \ttheta^{(s-1)}$\;
		$z_{0} \gets Gumbel(0,1)$\;
		$\bar{\ttheta} \gets Normal_D(\ttheta_0,\SSigma)$; \hspace{14em} \Comment{ \hspace{0.3em}     Proposal \eqref{eq:p1}}      
		\For{$p \in \{1,\dots,P\}$}{
			$\ttheta_p \gets Normal_D(\bar{\ttheta},\SSigma)$\;
			$z_{p} \gets Gumbel(0,1)$\;
		}
		$\hat{p} \gets \argmin_{p=0,\dots,P}\Big(f(p):= -\big(z_{p}+ \log\pi(\ttheta_{p}) \big)\Big)$\;  \hspace{10em}\Comment{\hspace{0.5em} $\order{\sqrt{P}}$ Alg \ref{alg:min} with warm-start at $p=0$.}
		$\ttheta^{(s)} \gets \ttheta_{\hat{p}}$\;
	}
	\Return{$\ttheta^{(1)}, \dots, \ttheta^{(S)}$}\ .
